%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Chris Pedersen} % Your name
\address{2706 Bay Dr. \\ Bradenton, Florida 34207} % Your address
\address{(941)~$\cdot$~313~$\cdot$~0085 \\ Chrispe1217@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{}
Dear IMG Academy,

I recently learned about your tutoring positions at IMG Academy through indeed.com and would like to be considered for this position. I have experience both tutoring and teaching physics as well as an extremely strong math background. Along with having taken a multitude of mathematics courses while getting my bachelors and masters degrees in physics I received a perfect 800 score on the math section of the SAT and nearly perfect 780 on the math section of the GRE. I believe I could be a great asset as a tutor and am able to cover most of the subjects in your job listing including Algebra, Geometry, Trigonometry, Pre-Calculus, Calculus, Physics, and SAT/ACT Mathematics.

Tutoring was one of the most rewarding experiences I had as a graduate student. Over the course of a semester working with students that were very behind in both their mathematics and physics knowledge I was able to truly help them and drastically improve their understanding and success in their classes. Being able to directly impact students' success through one on one or small group tutoring is a truly fulfilling experience and I was overjoyed when I heard many of the students who had been severely struggling before my tutoring received A's in their physics class.

I sincerely believe I would make an excellent addition to you tutoring program and look forward to hearing from you. Thank you for your consideration.

Sincerely,

Chris Pedersen




\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
